---
output: powerpoint_presentation
---

```{r, echo=FALSE}
params <- list()
params$set_title <- paste(indicator_key(), "Climate Presentation")
```

---
title: `r params$set_title`
date: "`r Sys.Date()`"
---


## Rainfall Plot

```{r, echo = FALSE, warning=FALSE}

rainfall_data <- rainfall_csv[rainfall_csv$adm0_name == indicator_key(),]

ggplot(data=rainfall_data, aes(x = year, y = mean)) +
  geom_line(aes(color = "#003870")) +
  xlab("Year") + 
  ylab("Annual Mean Values") +
  scale_y_continuous(limits = c(min(rainfall_data$mean), max(rainfall_data$mean))) +
  theme_classic() +
  geom_smooth(method = "lm", se=FALSE, size=0.4, aes(color = "red")) +
  scale_color_identity(name = " ",
                       breaks = c("#003870", "red"),
                       labels = c("Mean", "Trend"),
                       guide = "legend")
```          

## Rainfall Map

```{r, echo = FALSE, warning=FALSE}

shp <- subset(country_boundaries, adm0_name %in% c(indicator_key()))
shp <- sf:::as_Spatial(shp)
raster <- crop(precip_data1, extent(shp))

plot(raster, axes = FALSE, box = FALSE)
plot(shp, add=TRUE, axes = FALSE, box = FALSE)

```    

## Rainfall Data Information

About the data:
Rainfall data derived from the CHIRPS (Climate Hazard Group InfraRed Precipitation with Station data) depicts rainfall estimates from 1981- 2018 at a spatial resolution of about 5-km. Dataset merges satellite imagery with in-situ station data to create gridded rainfall time-series for trend analysis and seasonal drought monitoring. This dataset was produced with the methodological support provided the IFAD-WFP Climate Analysis Partnership. 
Source of the dataset: Climate Hazard Group of California, Santa Barbara.

## NDVI Plot

```{r, echo = FALSE, warning=FALSE}

ndvi_data <- ndvi_csv[ndvi_csv$adm0_name == indicator_key(),]

ggplot(data=ndvi_data, aes(x = year, y = mean)) +
  geom_line(aes(color = "#003870")) +
  xlab("Year") + 
  ylab("NDVI") +
  scale_y_continuous(limits = c(min(ndvi_data$mean), max(ndvi_data$mean))) +
  theme_classic() +
  geom_smooth(method = "lm", se=FALSE, size=0.4, aes(color = "red")) +
  scale_color_identity(name = " ",
                       breaks = c("#003870", "red"),
                       labels = c("Time Series", "Trend"),
                       guide = "legend")

```


## NDVI Map

```{r, echo=FALSE, warning=FALSE}

shp <- subset(country_boundaries, adm0_name %in% c(indicator_key()))
shp <- sf:::as_Spatial(shp)
raster <- crop(ndvi_tif, extent(shp))

plot(raster, axes = FALSE, box = FALSE)
plot(shp, add=TRUE, axes = FALSE, box = FALSE)

```

## NDVI Data Informtation

About the data:
Rainfall data derived from the CHIRPS (Climate Hazard Group InfraRed Precipitation with Station data) depicts rainfall estimates from 1981- 2018 at a spatial resolution of about 5-km. Dataset merges satellite imagery with in-situ station data to create gridded rainfall time-series for trend analysis and seasonal drought monitoring. This dataset was produced with the methodological support provided the IFAD-WFP Climate Analysis Partnership.


## Annual Minimum Temperature Plot

```{r, echo = FALSE, warning=FALSE}

mintemp_data <- mintemp_csv[mintemp_csv$adm0_name == indicator_key(),]

ggplot(data=mintemp_data, aes(x=year, y=mean_min)) +
  geom_line(aes(color = "#003870")) +
  xlab("Year") + 
  ylab("Temp (°C)") +
  scale_y_continuous(limits = c(min(mintemp_data$mean_min), max(mintemp_data$mean_min))) +
  theme_classic() +
  geom_smooth(method = "lm", se=FALSE, size=0.4, aes(color = "red")) +
  scale_color_identity(name = " ",
                       breaks = c("#003870", "red"),
                       labels = c("Minimum Temperature", "Trend Line"),
                       guide = "legend")

```

## Annual Minimum Temperature Map

```{r, echo = FALSE, warning=FALSE}

    shp <- subset(country_boundaries, adm0_name %in% c(indicator_key()))
    shp <- sf:::as_Spatial(shp)
    raster <- crop(mintemp_tif, extent(shp))

    plot(raster, axes = FALSE, box = FALSE)
    plot(shp, add=TRUE, axes = FALSE, box = FALSE)
    
```  

## Annual Minimum Temperature Data Information

About the data:
Vegetation Index (NDVI) data reflect both amount and health of vegetation. 
In areas of low rainfall where water is the limiting factor for vegetation growth, 
seasonal NDVI is closely linked to rainfall; this relationship gets progressively 
weaker as seasonal rainfall increases and factors other than water availability 
assume greater importance in controlling vegetation development. The NDVI data in 
use is from the NASA MODIS platforms Terra, which provide global coverage since 2001 
(Terra) at about 1Km resolution with a temporal frequency of 16 day periods. Methodological support provided the IFAD-WFP Climate Analysis Partnership Time period: 2001-2018.


```{r, echo = FALSE, warning=FALSE}

maxtemp_data <- maxtemp_csv[maxtemp_csv$adm0_name == indicator_key(),]

ggplot(data=maxtemp_data, aes(x = year, y = mean_max)) +
  geom_line(aes(color = "#003870")) +
  xlab("Year") + 
  ylab("Temp (°C)") +
  scale_y_continuous(limits = c(min(maxtemp_data$mean_max), max(maxtemp_data$mean_max))) +
  theme_classic() +
  geom_smooth(method = "lm", se=FALSE, size=0.4, aes(color = "red")) +
  scale_color_identity(name = " ",
                       breaks = c("#003870", "red"),
                       labels = c("Maximum Temperature", "Trend Line"),
                       guide = "legend")

```

## Annual Maximum Temperature Map

```{r, echo = FALSE, warning=FALSE}

    shp <- subset(country_boundaries, adm0_name %in% c(indicator_key()))
    shp <- sf:::as_Spatial(shp)
    raster <- crop(maxtemp_tif, extent(shp))

    plot(raster, axes = FALSE, box = FALSE)
    plot(shp, add=TRUE, axes = FALSE, box = FALSE)
    
``` 

## Annual Maximum Temperature Data Information

About the data:
Global mean min temperature data is based on the TerraClimate dataset of monthly climate for global terrestrial surfaces from 1958- 2017 at a spatial resolution of about 5-km. This data set was produced with the methodological support provided the IFAD-WFP Climate Analysis Partnership. Mean minimum temperature (°C) can be defined as the average daily minimum air temperature, for each month and as an annual statistic, calculated for each of the years of interest. Source of data: University of Idaho