---
header-includes: 
- \usepackage{xcolor}
- \usepackage{sectsty} \sectionfont{\centering}
geometry: margin = 1in
output: pdf_document
---

```{r, echo=FALSE}
params <- list()
params$set_title <- paste(indicator_key(), "Climate Fact Sheet")
```

---
title: `r params$set_title`
date: "`r Sys.Date()`"
---

The climate fact sheet allows easy visualization of processed country environmental and climate information generated in Google Earth Engine (GEE) and updated on a daily basis. Developed by the ICT GIS Solutions Team and the Environment, Climate and Gender Division (ECG) with the methodological support of the IFAD-WFP Climate Analysis Partnership.

***

# Mean Precipitation (MM)

```{r, echo=FALSE, fig.align="default", warning=FALSE, fig.show = "hold", out.width = "50%"}

rainfall_data <- rainfall_csv[rainfall_csv$adm0_name == indicator_key(),]

ggplot(data = rainfall_data, aes(x = year, y = mean)) +
  geom_line(aes(color = "#003870")) +
  xlab("Year") +
  ylab("Annual Mean Values") +
  scale_y_continuous(limits = c(min(rainfall_data$mean), max(rainfall_data$mean))) +
  theme_classic() +
  geom_smooth(method = "lm", se=FALSE, size=0.4, aes(color = "red")) +
  scale_color_identity(name = " ",
                       breaks = c("#003870", "red"),
                       labels = c("Mean", "Trend"),
                       guide = "legend")


spdf <- as(rainfall_react(), "SpatialPixelsDataFrame")
df <- as.data.frame(spdf)
colnames(df) <- c("value", "x", "y")

ggplot() +  
  geom_tile(data = df, aes(x = x, y = y, fill = value), alpha = 1) + 
  geom_polygon(data = shapefile_react(), aes(x = long, y = lat, group = group), 
               fill = NA, color = "grey50", size = 0.25) +
  scale_fill_viridis(option = "magma") +
  coord_equal() +
  theme_void() +
  theme(legend.position = "bottom") +
  theme(legend.key.width = unit(2, "cm"))


```          

About the data:
Rainfall data derived from the CHIRPS (Climate Hazard Group InfraRed Precipitation with 
Station data) depicts rainfall estimates from 1981- 2018 at a spatial resolution of about 5-km. Dataset merges satellite imagery with in-situ station data to create gridded rainfall time-series for trend analysis and seasonal drought monitoring. This dataset was produced with the methodological support provided the IFAD-WFP Climate Analysis Partnership.

\newpage

# Mean NDVI

```{r, echo=FALSE, fig.align="default", warning=FALSE, fig.show = "hold", out.width = "50%"}

ndvi_data <- ndvi_csv[ndvi_csv$adm0_name == indicator_key(),]

ggplot(data=ndvi_data, aes(x = year, y = mean)) +
  geom_line(aes(color = "#003870")) +
  xlab("Year") +
  ylab("NDVI") +
  scale_y_continuous(limits = c(min(ndvi_data$mean), max(ndvi_data$mean))) +
  theme_classic() +
  geom_smooth(method = "lm", se=FALSE, size=0.4, aes(color = "red")) +
  scale_color_identity(name = " ",
                       breaks = c("#003870", "red"),
                       labels = c("Time Series", "Trend"),
                       guide = "legend")



spdf <- as(ndvi_react(), "SpatialPixelsDataFrame")
df <- as.data.frame(spdf)
colnames(df) <- c("value", "x", "y")

ggplot() +  
  geom_tile(data = df, aes(x = x, y = y, fill = value), alpha = 1) + 
  geom_polygon(data = shapefile_react(), aes(x = long, y = lat, group = group), 
               fill = NA, color = "grey50", size = 0.25) +
  scale_fill_viridis(option = "magma") +
  coord_equal() +
  theme_void() +
  theme(legend.position = "bottom") +
  theme(legend.key.width = unit(2, "cm"))

```

About the data:
Vegetation Index (NDVI) data reflect both amount and health of vegetation. 
In areas of low rainfall where water is the limiting factor for vegetation growth, 
seasonal NDVI is closely linked to rainfall; this relationship gets progressively 
weaker as seasonal rainfall increases and factors other than water availability 
assume greater importance in controlling vegetation development. The NDVI data in 
use is from the NASA MODIS platforms Terra, which provide global coverage since 2001 
(Terra) at about 1Km resolution with a temporal frequency of 16 day periods. Methodological support provided the IFAD-WFP Climate Analysis Partnership Time period: 2001-2018.


\newpage

# Mean Annual Minimum Temperature (°C)

```{r, echo = FALSE, warning = FALSE, fig.align="default", fig.show = "hold", out.width = "50%"}

mintemp_data <- mintemp_csv[mintemp_csv$adm0_name == indicator_key(),]

ggplot(data=mintemp_data, aes(x=year, y=mean_min)) +
  geom_line(aes(color = "#003870")) +
  xlab("Year") +
  ylab("Temp (°C)") +
  scale_y_continuous(limits = c(min(mintemp_data$mean_min), max(mintemp_data$mean_min))) +
  theme_classic() +
  geom_smooth(method = "lm", se=FALSE, size=0.4, aes(color = "red")) +
  scale_color_identity(name = " ",
                       breaks = c("#003870", "red"),
                       labels = c("Minimum Temperature", "Trend Line"),
                       guide = "legend")

spdf <- as(mintemp_react(), "SpatialPixelsDataFrame")
df <- as.data.frame(spdf)
colnames(df) <- c("value", "x", "y")

ggplot() +  
  geom_tile(data = df, aes(x = x, y = y, fill = value), alpha = 1) + 
  geom_polygon(data = shapefile_react(), aes(x = long, y = lat, group = group), 
               fill = NA, color = "grey50", size = 0.25) +
  scale_fill_viridis(option = "magma") +
  coord_equal() +
  theme_void() +
  theme(legend.position = "bottom") +
  theme(legend.key.width = unit(2, "cm"))

```

# Trend in Annual Minimum Temperature (°C)

```{r, echo = FALSE, warning = FALSE, fig.align="default", fig.show = "hold", out.width = "50%"}

spdf <- as(mintemp_trend_country_react(), "SpatialPixelsDataFrame")
df <- as.data.frame(spdf)
colnames(df) <- c("value", "x", "y")

ggplot() +  
  geom_tile(data = df, aes(x = x, y = y, fill = value), alpha = 1) + 
  geom_polygon(data = shapefile_react(), aes(x = long, y = lat, group = group), 
               fill = NA, color = "grey50", size = 0.25) +
  scale_fill_viridis(option = "magma") +
  coord_equal() +
  theme_void() +
  theme(legend.position = "bottom") +
  theme(legend.key.width = unit(2, "cm"))

```

About the data:
Global mean min temperature data is based on the TerraClimate dataset of monthly climate for global terrestrial surfaces from 1958- 2017 at a spatial resolution of about 5-km. This data set was produced with the methodological support provided the IFAD-WFP Climate Analysis Partnership. Mean minimum temperature (°C) can be defined as the average daily minimum air temperature, for each month and as an annual statistic, calculated for each of the years of interest. Source of data: University of Idaho


\newpage


# Mean Annual Maximum Temperature (°C)

```{r, echo=FALSE, fig.align="default", warning=FALSE, fig.show = "hold", out.width = "50%"}

maxtemp_data <- maxtemp_csv[maxtemp_csv$adm0_name == indicator_key(),]

ggplot(data=maxtemp_data, aes(x = year, y = mean_max)) +
  geom_line(aes(color = "#003870")) +
  xlab("Year") +
  ylab("Temp (°C)") +
  scale_y_continuous(limits = c(min(maxtemp_data$mean_max), max(maxtemp_data$mean_max))) +
  theme_classic() +
  geom_smooth(method = "lm", se=FALSE, size=0.4, aes(color = "red")) +
  scale_color_identity(name = " ",
                       breaks = c("#003870", "red"),
                       labels = c("Maximum Temperature", "Trend Line"),
                       guide = "legend")

spdf <- as(maxtemp_react(), "SpatialPixelsDataFrame")
df <- as.data.frame(spdf)
colnames(df) <- c("value", "x", "y")

ggplot() +  
  geom_tile(data = df, aes(x = x, y = y, fill = value), alpha = 1) + 
  geom_polygon(data = shapefile_react(), aes(x = long, y = lat, group = group), 
               fill = NA, color = "grey50", size = 0.25) +
  scale_fill_viridis(option = "magma") +
  coord_equal() +
  theme_void() +
  theme(legend.position = "bottom") +
  theme(legend.key.width = unit(2, "cm"))

```

# Trend in Annual Maximum Temperature (°C)

```{r, echo = FALSE, warning = FALSE, fig.align="default", fig.show = "hold", out.width = "50%"}

spdf <- as(maxtemp_trend_country_react(), "SpatialPixelsDataFrame")
df <- as.data.frame(spdf)
colnames(df) <- c("value", "x", "y")

ggplot() +  
  geom_tile(data = df, aes(x = x, y = y, fill = value), alpha = 1) + 
  geom_polygon(data = shapefile_react(), aes(x = long, y = lat, group = group), 
               fill = NA, color = "grey50", size = 0.25) +
  scale_fill_viridis(option = "magma") +
  coord_equal() +
  theme_void() +
  theme(legend.position = "bottom") +
  theme(legend.key.width = unit(2, "cm"))

```

About the data:
Global mean max temperature data is based on the TerraClimate dataset of monthly climate for global terrestrial surfaces from 1958- 2017 at a spatial resolution of about 5-km. This data set was produced with the methodological support provided the IFAD-WFP Climate Analysis Partnership. Mean maximum temperature (°C) can be defined as the average daily maximum air temperature, for each month and as an annual statistic, calculated for each of the years of interest. Source of data: University of Idaho.


